### 2012-12-05 inst/examples/comparing-methods.Rmd
illustration of configuring some of the parameters and accessing the correct output in tgp #6

```{r}
require(MASS)
require(ggplot2)
require(kernlab)
require(nonparametricbayes)
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"), comment=NA, tidy=FALSE)
theme_set(theme_bw())
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
```

>>>>

```{r}
require(MASS)
require(ggplot2)
require(kernlab)
require(nonparametricbayes)
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"), comment=NA, tidy=FALSE)
theme_set(theme_bw())
theme_update(panel.background = element_rect(fill = "transparent",colour = NA))
```

### 2012-12-05 inst/examples/mcmc-gp.Rmd
illustration of configuring some of the parameters and accessing the correct output in tgp #6

```{r results="hide"}
knit("beverton_holt_data.Rmd")
true <- data.frame(x = X, y = sapply(X, f, 0, p))
```

```{r}
gp <- bgp(X=obs$x, XX=X, Z=obs$y)
```

@@

```{r}
center <- tgp:::tgp.choose.center(gp, "mean")
Z.mean <- center$Z
X_vals <- center$X[, 1]
o <- order(X_vals)
Zb.q1 <- Z.mean + 1.96 * sqrt(c(gp$Zp.ks2, gp$ZZ.ks2))
Zb.q2 <- Z.mean - 1.96 * sqrt(c(gp$Zp.ks2, gp$ZZ.ks2))
V <- c(gp$Zp.ks2, gp$ZZ.ks2)[o]
dat <- data.frame(x=X_vals[o], y=Z.mean[o], ymin=Zb.q1[o], ymax=Zb.q2[o])
```

@@

>>>>

```{r results="hide"}
knit("~/Documents/code/nonparametric-bayes/inst/examples/beverton_holt_data.Rmd")
true <- data.frame(x = x_grid, y = sapply(x_grid, f, 0, p))
XX <- as.matrix(x_grid)
X <- as.matrix(obs$x)
Z <- as.matrix(obs$y)
```

Normalize data to the unit (hyper)cube.

```{r, include=FALSE, eval=FALSE}
unit_norm <- function(x, M=NULL, m=NULL, invert=FALSE){
  if(is.null(M)){
    M <- max(x) 
    m <- min(x)
    message(paste("Max M = ", M, "min m = ", m))
  }

  if(!invert) {
    (x-m)/(M-m)
  } else {
    (M-m)*x+m
  }
}
XX = unit_norm(XX)
X = unit_norm(X)
Z = unit_norm(Y)
```

```{r}
gp <- bgp(X=X, XX=XX, Z=Z, meanfn="constant", bprior="b0", BTE=c(1000,6000,2), m0r1=FALSE, verb=4, corr="exp", trace=TRUE, s2.p=c(5,10), tau2.p=c(5,10), s2.lam="fixed", tau2.lam="fixed")
```

Take a look at the trace

```{r}
names(gp$trace$XX[[1]])
dim(gp$trace$XX[[1]])
gp$trace$XX[[1]][1,]
gp$trace$XX[[1]][2500,]
````

* `index` is the sampling point (from `BTE`, we see we sample starting at step 1000 and ending at step 6000, recording every 2 steps, so there are $(T-B)/E = 2500$ index points).

* `lambda`
* `s2`
* `tau2`
* `beta0`
* `nug`
* `d`

@@

```{r}

dat <- data.frame(x    = gp$XX[[1]], 
                 y    = gp$ZZ.km, 
                 ymin = gp$ZZ.km - 1.96 * sqrt(gp$ZZ.ks2), 
                 ymax = gp$ZZ.km + 1.96 * sqrt(gp$ZZ.ks2))

@@

is mean ZZ.mean or ZZ.km?  is the var I want ZZ.s2 or ZZ.ks2?)  I want the kreiging values (km, ks2).  The others slightly don't agree with the above.  We do this by comparing to the plotted option (which handles the rescaling(?) from `choose.center` first).

```{r}
center <- tgp:::tgp.choose.center(gp, "mean")
Z.mean <- center$Z
X_vals <- center$X[, 1]
o <- order(X_vals)
Zb.q1 <- Z.mean + 1.96 * sqrt(c(gp$Zp.ks2, gp$ZZ.ks2))
Zb.q2 <- Z.mean - 1.96 * sqrt(c(gp$Zp.ks2, gp$ZZ.ks2))
V <- c(gp$Zp.ks2, gp$ZZ.ks2)[o]
df <- data.frame(x=X_vals[o], y=Z.mean[o], ymin=Zb.q1[o], ymax=Zb.q2[o])

raw <- data.frame(x    = gp$XX[[1]], 
                 y    = gp$ZZ.mean, 
                 ymin = gp$ZZ.mean - 1.96 * sqrt(gp$ZZ.s2), 
                 ymax = gp$ZZ.mean + 1.96 * sqrt(gp$ZZ.s2))

p1 + geom_ribbon(aes(x,y, ymin=ymin, ymax=ymax), fill="red", alpha=.1, data=df) + geom_line(aes(x,y), col="red", data=df)  + geom_ribbon(aes(x,y, ymin=ymin, ymax=ymax), fill="blue", alpha=.1, data=raw) + geom_line(aes(x,y), col="blue", data=raw) 
```
